---
title: "Into the Text Prediction App"
author: "Diogenes Cruz Figueroa García"
date: "4/5/2020"
output: html_document
---

```{r setup, include=FALSE, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE, error = FALSE, message = FALSE, warning = FALSE)
```


# 1 Synopsis
In this document, I show the approach I followed towards generating the shiny 
app for the Coursera - JHU Data Science Specialization Capston. The app is a 
simple text predictor which sugests a number of words based on what's been 
written before, using some Natural Language Processing. [Here](insert.shiny) 
you can find the Shiny App, whereas the pitch for the app can be found 
[here](pitch)

# 2 Background
The last report I submited was the mileston report, which can be seen in RPubs 
clicking on the following 
[link](https://rpubs.com/DiogenesCFG/C-JHU_Capstone_Week2_Milestone_Report). 
Since then, I have started almost from zero, since the methods I was using to 
clean the data and generate ngrams was innecessarily long, and then I learned 
about the package `tidytext`, which has a very easy function for generating 
ngrams, and ending up with a tidy table which can be then easily used for 
training our text prediction app. So let's get to it.

# Getting and Cleaning Data
We already downloaded our data, and cleaned it, but as I said, I wanted to 
start fresh from zero... well, not downloading the data again, but processing 
it and generating our ngrams. Besides, last time, I treated separately the 
text from blogs, news and twitter. Here, I'll merge all the data bases samples 
from the beginning to avoid any complication.

Also, in my Predictive_Text.Rmd` document, which can also be found in my 
[github account](https://github.com/DiogenesCFG/Coursera_Capstone_Project) 
you can see how I got the data. But I won't be downloading it again. For obious 
reasons. So, let's get to it.

# Getting, cleaning and processing data

Before starting, I'll load all packages I'll be using here... well, not all 
of them are actually being used, but in the trial and error, I might have 
loaded a package that didn't make the final cut, but it's still interesting 
to have a look at them and see what they do.

```{r load_packages}
library(LaF); library(dplyr); library(tidyr); library(ggplot2); library(tm);
library(tokenizers); library(stringi); library(quanteda); library(data.table); 
library(stringr); library(knitr); library(caret); library(tidytext)
```

The first step is to get our data. We'll go straight to it, and get only a 
sample of the data from blogs, news and twitter, corresponding to 5% of the 
lines in each data set, and merge them together. Though this may seem small, 
we'll still end up with over 150 thousand lines, which, when translated to 
quadgrams, will give us enough information to train a simple text prediction 
app.

```{r Getting_data}
# Set the path in our directory where the data is stored.

twitterFile <- ".\\Data\\final\\en_US\\en_US.twitter.txt"
blogsFile <- ".\\Data\\final\\en_US\\en_US.blogs.txt"
newsFile <- ".\\Data\\final\\en_US\\en_US.news.txt"

# Get whole data set
twitter <- readLines(twitterFile, encoding = "UTF-8", skipNul = TRUE)
blogs <- readLines(blogsFile, encoding = "UTF-8", skipNul = TRUE)
news <- readLines(newsFile, encoding = "UTF-8", skipNul = TRUE)

# Convert to data frame to better treat them and merge them
twitter <- data_frame(text = twitter)
blogs <- data_frame(text = blogs)
news <- data_frame(text = news)

# Getting a sample from our data
set.seed(122814)
s_twitter <- sample_n(twitter, nrow(twitter) * .2)
s_twitter <- mutate(s_twitter, source = "twtitter")

s_blogs <- sample_n(blogs, nrow(blogs) * .2)
s_blogs <- mutate(s_blogs, source = "blogs")

s_news <- sample_n(news, nrow(news) * .2)
s_news <- mutate(s_news, source = "news")

# Merging the dataset samples
sample <- bind_rows(s_twitter, s_blogs, s_news)

# We're going to work from now on only with the merged sample, so let's clear everything else.
rm(twitterFile, blogsFile, newsFile, twitter, blogs, news, s_twitter, 
   s_blogs, s_news)
```

Now we have a single dataset consisting of `r nrow(sample)` lines from twitter, 
blogs and news sites. We then need to clean the data. Since there is a 
difference between caps and lowercase letters, we'll convert everything to 
lowercase to get more accurate results. We'll also get rid of punctuation 
marks, and special symbols ($#%&! and what not). Once we have that, we can 
procede to get our ngrams.

```{r cleaning_the_data}
# Convert to ASCII to avoid special characters
sample$text <- iconv(sample$text, from = "UTF-8", to = "ASCII//TRANSLIT")
# Get only lower caps
sample$text <- tolower(sample$text)
# Since numbers are difficult to predict and add little to no information for 
# predicting, we'll also get rid of those
sample$text <- gsub("[0-9]", "", sample$text)
# I had a dilema here of what to do with apostrophes,... at the end, I figured 
# I will just treat them as empty characters
sample$text <- gsub("'", "", sample$text)
# Remove special characters
sample$text <- str_replace_all(sample$text, "[^[:alnum:]]", " ")
# Remove double spacing
sample$text <- str_squish(sample$text)
```

Now we have a clean data base consisting of normal characters and sentences.
In total, we have 166,833 lines, each line being either a complete tweet, a 
complete news article, or a complete blog entry. Such a number may not seem 
as much, but when converted to ngrams, our number of observations will 
increase dramatically. In my mileston report, I created the unigrams and 
bigrams without stopwords (common words such as "the", "and" "of"...) that 
appear to often to give any information on word frequency. However, for a 
text prediction app, this words have to appear, otherwise our text prediction 
app will end up creating sentences like "going house get something drink" 
instead of a more readable sentence like "I'm going to my house now to get 
something to drink." The former sentence is still understandable, but c'mon, 
nobody talks like that, except maybe 
[Kevin, from The Office](https://www.youtube.com/watch?v=_K-L9uhsBLM). But 
we don't want to get into that.

So let's get to geting our ngrams. We'll use the `unnest_tokens()` function 
from the `tidytext` package, which makes use of the `tokenizers`package. 
Last time I did't know this function existed in this package, so I just 
created my own function that sepparated the ngrams, and gave the relative 
frequency of each one, collapsed them and what not, but it took a lot of 
memory and time to compile, whereas `unnest_tokens()` uses way less resources, 
and I can collapse and get the relative frequency later.

```{r getting_ngrams}
# Unigrams (Or, you know, as common people know them, words)
ngram1 <- sample %>% 
     unnest_tokens(unigram, text)
# Bigrams
ngram2 <- sample %>% 
     unnest_tokens(bigram, text, token = "ngrams", n = 2)
# Trigrams
ngram3 <- sample %>% 
     unnest_tokens(trigram, text, token = "ngrams", n = 3)
# Quadgrams
ngram4 <- sample %>% 
     unnest_tokens(quadgram, text, token = "ngrams", n = 4)
```

We now have four data bases consisting of observations of ngrams, which can 
be repeated. But we are more interested in the frequency of each ngram, so as 
to better predict the word that will follow some combinations of words. So 
we'll make our tables in this sense.

```{r collapsing_ngrams}
ngram1 <- ngram1 %>%
     count(unigram) %>%  
     mutate(proportion = n / sum(n)) %>%
     arrange(desc(proportion)) %>%  
     mutate(coverage = cumsum(proportion))
ngram2 <- ngram2 %>%
     count(bigram) %>%  
     mutate(proportion = n / sum(n)) %>%
     arrange(desc(proportion)) %>%  
     mutate(coverage = cumsum(proportion))
ngram3 <- ngram3 %>%
     count(trigram) %>%  
     mutate(proportion = n / sum(n)) %>%
     arrange(desc(proportion)) %>%  
     mutate(coverage = cumsum(proportion))
ngram4 <- ngram4 %>%
     count(quadgram) %>%  
     mutate(proportion = n / sum(n)) %>%
     arrange(desc(proportion)) %>%  
     mutate(coverage = cumsum(proportion))
```

Now that we have our ngrams, we'll separate the words. The way we'll do this 
is consider the last word to be the objective, and count backwards the 
preceding words. For example, if we have an ngram "this is the last", the 
word "last" will be in the "word" variable, whereas "the" will be "word-1", 
that is, one position to the left, "is" will be in "word-2" and "this" in 
"word-3". 

Why do it this way? It just makes way more sense in my head, since we'll be 
predicting a word using the previous ones. So, let's do this for all the 
ngrams.

```{r separating_words}
# The unigram needs no separation, but let's just rename the column
names(ngram1)[1] <- "word"

# Now, we separate an name the rest of the ngrams
ngram2 <- ngram2 %>% 
     separate(bigram, 
              c("word_1", "word"), 
              sep = " ")
ngram3 <- ngram3 %>% 
     separate(trigram, 
              c("word_2", "word_1", "word"), 
              sep = " ")
ngram4 <- ngram4 %>% 
     separate(quadgram, 
              c("word_3", "word_2", "word_1", "word"), 
              sep = " ")
```

Now that we have our separated databases, let's save them as they are, to 
avoid all the hastle again, and we can use these data bases for prediction.

```{r save_separated_ngrams}
if(!file.exists(".\\Separated Ngrams")){dir.create(".\\Separated Ngrams")}

saveRDS(ngram1, ".\\Separated Ngrams\\ngram1.rds")
saveRDS(ngram2, ".\\Separated Ngrams\\ngram2.rds")
saveRDS(ngram3, ".\\Separated Ngrams\\ngram3.rds")
saveRDS(ngram4, ".\\Separated Ngrams\\ngram4.rds")
```

We can now use these ngrams to make a simple text prediction model. What we 
are going to do is to take a text as an input, with at least `n-1` words, where 
`n > 2`. We'll look in the ngram with `n`tokens, and see if there is a match 
for the phrase, and take the most frequent ngram that shows said match for the 
first `n-1` words. The function then will display the `n`th word of such 
ngram. In the case there is no match, the function will remove the first word 
of the phrase, and use the same procedure with the `n-1` tokens ngram. And so 
on. So, let's do this. With an empty input, suggestions will simply be the 
most common used words.

```{r building_prediction_functions}
# I want my app to give three suggestions.
# In the worst case scenario where no prediction can be made, our program is 
# goint to suggest the three most common words.
top3 <- c(as.character(ngram1[1, 1]), 
            as.character(ngram1[2, 1]), 
            as.character(ngram1[3, 1]))

# Predicting from the last word, with bigrams
pred2 <- function(textInput){
     # Getting the last word
          firstWord <- tail(strsplit(textInput, split = " ")[[1]], 1)[1]
     Filtered <- filter(ngram2, word_1 == firstWord)[1:3, ]
     Suggestion <- Filtered[1:3, 2]
     if(is.na(Suggestion[1, 1])){
          print(top3)
     } else { 
          c(as.character(Suggestion[1, 1]), 
            as.character(Suggestion[2, 1]), 
            as.character(Suggestion[3, 1])
          )
     }
}

# Predicting from the last two words, with trigrams
pred3 <- function(textInput){
     # Getting the last two words
          firstWord <- tail(strsplit(textInput, split = " ")[[1]], 2)[2]
          secondWord <- tail(strsplit(textInput, split = " ")[[1]], 2)[1]
     Filtered <- filter(ngram3, word_1 == firstWord & 
                             word_2 == secondWord)[1:3, ]
     Suggestion <- Filtered[1:3, 3]
     if(is.na(Suggestion[1, 1])){
          pred2(textInput)
     } else { 
          c(as.character(Suggestion[1, 1]), 
            as.character(Suggestion[2, 1]), 
            as.character(Suggestion[3, 1])
          )
     }
}

# Predicting from the last three words, with quadgrams
pred4 <- function(textInput){
     # Getting the last three words words
     firstWord <- tail(strsplit(textInput, split = " ")[[1]], 3)[3]
     secondWord <- tail(strsplit(textInput, split = " ")[[1]], 3)[2]
     thirdWord <- tail(strsplit(textInput, split = " ")[[1]], 3)[1]
     Filtered <- filter(ngram4, word_1 == firstWord & 
                             word_2 == secondWord & 
                             word_3 == thirdWord)[1:3, ]
     Suggestion <- Filtered[1:3, 4]
     if(is.na(Suggestion[1, 1])){
          pred3(textInput)
     } else { 
          c(as.character(Suggestion[1, 1]), 
            as.character(Suggestion[2, 1]), 
            as.character(Suggestion[3, 1])
          )
     }
}

```

In the last chunk I created 3 functions that predict the next word of a phrase 
based on the previous word: 
* `pred2`takes the last word of the phrase, and matches it with the first word 
of the bigrams. Then it takes the most common words that follow that last word 
of our original phrase and gives it as an output. In case no match is found, 
the function just suggests the most common words overall from our unigrams.
* `pred3` takes the last two words of the phrase, and matches it with exactly 
the first two words of the trigrams. Then it takes the most common words that 
follow that last two words of our original phrase and gives them as an output. 
In case no match is found, the function redirects the input phrase to the 
`pred2` function.
* `pred4` takes the last three words of the phrase, and matches it with 
exactly the first three words of the quadgrams. Then it takes the most common 
words that follow that last three words of our original phrase and gives them 
as an output. In case no match is found, the function redirects the input 
phrase to the `pred3` function.

Notice that that from either of these functions, a suggestion will be given, 
since they will redirect to a simpler function, until only the most common 
words are given as outputs in case no other match is made.

The last step is to build a function that chooses from which `pred`function to 
start with, in order to save time (and avoid an error message). This function 
will be quiet simple, and will only take the input phrase, see how many words 
it has, and choose the `pred` function accordingly: `pred2`if only one word is 
given, `pred3` if only two words are given, and `pred4`if 3 or more words are 
given. This function will also suggest the most common three words in case the 
input is empty. This function will start cleaning the prhase so that when the 
input goes into the `pred` functions, a match can be made. Since the function 
that will be directly used will be this `predictText()` function, there is no 
need to repeat the text cleaning procedure in the `pred` functions. 

```{r choose_pred_function}
predictText <- function(Input){
     # First, clean the text
     textInput <- tolower(Input)
     textInput <- gsub("[0-9]", "", textInput)
     textInput <- gsub("'", "", textInput)
     textInput <- str_replace_all(textInput, "[^[:alnum:]]", " ")
     textInput <- str_squish(textInput)
     # Now, count the number of words in the phrase
     inputLength <- str_count(textInput, '\\w+')
     if(inputLength == 0){
          top3
     } else if(inputLength == 1){
          pred2(textInput)
     } else if(inputLength == 2){
          pred3(textInput)
     } else {
          pred4(textInput)
     }
}
```

So that's our function for getting a prediction for the next word from our text prediction.